Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-20 paper.tex
fixed a typo

\begin{algorithm}
\caption{Algorithm: Incentivizing Exploration}
\label{Alg1}
\begin{algorithmic}
\STATE Set n = 1 to denote the round number;
\FOR{ $t = 1, 2, 3, \cdots$}{
	\IF{the myopic probability of pulling an arm is less than $n^{-1}$ and we haven’t pulled that arm in this round}
	\STATE{ we pay whatever it takes to incentivize that arm}\ELSE 
		\STATE {let the agents play myopically}\ENDIF
		\STATE $n = min_{i} N(i,t)$
}\ENDFOR

@@

\begin{theorem}
The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2 m + M m^2\log(T))$.
\label{rst:regret}
\end{theorem}

@@

\begin{algorithm}
\caption{Algorithm: Incentivizing Exploration Revised}
\label{Alg2}
\begin{algorithmic}
\STATE Set n = 1 to denote the round number;
\FOR{ $t = 1, 2, 3, \cdots$}{
	\IF{the myopic probability of pulling an arm $i$ is less than $n^{-1}$ and we haven’t pulled that arm $i$ in this round (if there are multiple such arms, pick one randomly)}
	\STATE{Offer payment $c_{i,t}=\inf\{c: P(\theta\sim F: \theta\cdot u_{i,t}+c>max_{j}\theta\cdot u_{j,t})>n^{-1}\}$}\ELSE 
		\STATE {let the agents play myopically}\ENDIF
		\STATE $n = min_{i} N(i,t)$
}\ENDFOR

>>>>

\begin{algorithm}
\caption{Algorithm: Incentivizing Exploration}
\label{Alg1}
\begin{algorithmic}
\STATE Set n = 1 to denote the round number;
\FOR{ $t = 1, 2, 3, \cdots$}{
	\IF{the myopic probability of pulling an arm is less than $n^{-1}$ and no agents have pulled that arm in this round (break ties randomly)}
	\STATE{ we pay whatever it takes to incentivize that arm}\ELSE 
		\STATE {let the agents play myopically}\ENDIF
		\STATE $n = min_{i} N(i,t)$
}\ENDFOR

@@

\begin{theorem}
The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2 m + M m^2(\log(T))^2)$.
\label{rst:regret}
\end{theorem}

@@

\begin{algorithm}
\caption{Algorithm: Incentivizing Exploration Revised}
\label{Alg2}
\begin{algorithmic}
\STATE Set n = 1 to denote the round number;
\FOR{ $t = 1, 2, 3, \cdots$}{
	\IF{the probability of pulling an arm $i$ is less than $n^{-1}$ and no agents have pulled that arm in this round (break ties randomly)}
	\STATE{Offer payment $c_{i,t}=\inf\{c: P(\theta\sim F: \theta\cdot u_{i,t}+c>max_{j}\theta\cdot u_{j,t})>n^{-1}\}$}\ELSE 
		\STATE {let the agents play myopically}\ENDIF
		\STATE $n = min_{i} N(i,t)$
}\ENDFOR
